%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{multicol}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Changhyun Lyoo} % Your name
\address {Woosung Apt. 109-106, 13 Sinheung-ro, Mokpo-si, South Korea, 58690} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+82)~10~6397~9396 \\  changhyunlyoo@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Educational Experience}
{\bf Handong Global University} \hfill 
\\  B.E. degree, February 2021 \hfill { Overall GPA: 3.31/4.5}
\\ Majors: ICT Convergence and Management
%Minor in Linguistics 
%\smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

{\bf \MakeUppercase {Skills and Other Information} % Section title
  \sectionlineskip
  \hrule
  }
\begin{multicols}{2}
%\begin{list}{$\cdot$}{\leftmargin=0.9em}
{\bf Skills}
  \\Microsoft Office literacy
  \\Java(Basic), Python(Intermediate) 
  \\HTML(Basic), CSS(Basic)
\\{\bf Military Service}
\\ Enlisted in the marine in September 2014
 \\ Honorably discharged from the marine in June 2016%\end{list}
\end{multicols}{}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\begin{rSubsection}{HGU}{December 2019 - May 2020}{Research Project, funded by National Research Foundation of Korea}{}
\item Development of Simulation models for municipal waste management system using Discrete Event System formalism.
\item User Interface development of the waste management system simulator using Qt for Python (PySide2).
\item Analysis of simulation data to support the decision makers for municipal solid waste management system.
\end{rSubsection}
% 여기에 우간다에서 프로젝트한것 문제해결능력등
\begin{rSubsection}
{HGU}{March 2018 - December 2019}{Cross-major Research Academy In Serving The other 90\%}{}
\item Prepared an income increase project for farmers' co-operative during the semester and visited Uganda during the vacation to carry out the project.
\item Helped to form a partnership between co-operative and NGO by connecting them.
\item Trained co-operative leaders about the management knowledge needed for actual business operations.
\item Solved the problems of co-operative-owned factory by comparing it with the case of other factories.

\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{Relevant Courses}
\itab{\textbf{Core Courses}} \tab{}  \tab{}
% 한줄로 역량, 성적 웹= pass 이지만 실제로 활용하고있다.O
\\ \itab{Data Management and Application(Data Structures \& 
Algorithms) Grade:A+} 
\\ \itab{System Engineering(Requirement Analysis and Design, Technical Document) Grade:A+} 
\\ \itab{Human Factors and Ergonomics(Human Factors, Ergonomics and Usability Engineering) Grade:A0}
%\\ \itab{C Programming(C Language & Structured Programming Approach) Grade:B+} \tab{}  \tab{}
\\ \itab{Special Topic of ICT Convergence(Cloud Infrastructure \& Business) Grade:P} \tab{} \tab{}
\\ \itab{Financial Management(Corporate finance, Financial markets, \& Investment) Grade:A+} \tab{}  \tab{}
\\ \itab{Production and Operations Management(Measure and Improve Performance of Operation) Grade:B0}\tab{} \tab{}

% \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Presentation and publication}

\begin{rSubsection}{International Conference}{}{}
\item {\underline{Chang Hyun Lyoo},  Jin Ho Jung, Chang Beom Choi and Eun Young Kim, ``Modeling and Simulation of Municipal Solid Waste Management System Based on Discrete Event System Specification", Symp. Simulation 
Architecture, Urban Design (SimAUD), May 2020.}
\end{rSubsection}


\end{rSection}
\end{document}
